### 2022-07-05 chapters/benchmarking/conclusion.tex
refactoring : revert the changes for the benchmarking protocol chapter

>>>>

\subsection{Extension}
We propose to extend the benchmarking framework suggested by the \emph{Collaboratory on Experimental Evaluation of Software and Systems in Computer Science}\footnote{\url{http://evaluate.inf.usi.ch/}} to address those limitations.
Instead of only presenting the four primary aspects of their guidelines that were mentioned in state of the art~\ref{sec:soa_reproducibility}, we propose an abstract model to describe an empirical experiment:

\emph{context}: the hardware and the software configuration for the actual experiment, the purpose of this part is to provide extra information to help readers have a better judgement on the results and to be able reproduce the experiment while diminishing the impact of the external factor . 
An \emph{orchestrator} which its job to run the experiment. 
The orchestrator provides three interfaces:

Workload interface  : Wich provides a set of functions that should be implemented by the workload  and called by the each candidate in the experiment. 
Observer interface : provides a set of metrics that are collected by the orchestrator during the expermentation. note that some of those metrics are external, such the energy consumption of the system , execution time, execution stack ..etc .

Figure\ref{fig:benchmarkingprotocol} explains in detail the relation ship within each component of the Protocol. 
First of all, we should start with the orchestrator which is the kernel of the experiment. Most of the time this kernel should represent the constants parts of the experiment. 
The orchestrator is responsible for the following  for the coordination between the workload and the candidate, therefore it provides an interface that is implemented by each workload. 
Later this interface will be provided to each candidate by the orchestrator. Like this we will remove any bias of dependecy between the workload and the candidates, which will alow us to extend both parts without any change in the code. 
Instead of retrieving the data directly from the experiment, we suggest to use an observator to allow the extension of the metrics, this observer in general should be outside the experiment to be able to gather as many informations without impacting the the code.  
\begin{figure}[!htb]
    \center{\includegraphics[width=\linewidth]{imgs/benchmarkingprotocol}}
    \caption{Benchmarking protocol}\label{fig:benchmarkingprotocol}
\end{figure}

### 2022-07-05 chapters/benchmarking/experiment.tex
refactoring : revert the changes for the benchmarking protocol chapter

% for each aspect we present a set of guidelines and tools.
%% This is a conclusion maaan  !! 
\section{Taming the energy variation for the benchmarking protocol}

@@

%% TODO: Proof read this paragraph

>>>>

% for each aspect we present a set of guidelines and tools.
%% This is a conclusion maaan  !! 
\section{Taming the energy variation for the benchmarking protocol}\label{sec:taming-the-energy-variation}

@@

\subsection{Docker \& Accuracy}
As the state of the art assesses the impact of Docker on the energy consumption, one can also consider its impact on accuracy.
In other words:\\
\textbf{RQ:} does Docker affect the energy variation of the experiments?

To answer this question we conducted a preliminary experiment by running the same benchmarks \textsf{LU}, \textsf{CG} and \textsf{EP} in a Docker container and a flat binary format on 3 nodes of the cluster \textsf{Dahu} to assess if Docker induces an additional variation.
Figure~\ref{fig:docker} reports that this is not the case, as the energy consumption variation does not get noticeably affected by Docker while running a same compiled version of the benchmarks at 5\,\%, 50\,\% and 100\,\% workloads.
In fact, while Docker increases the energy consumption due to the extra layer it implements~\cite{eddie_antonio_santos_how}, it does not noticeably affect the energy variation.
The \emph{standard deviation} (STD) is even slightly smaller ($STD_{Docker}=192 mJ$,$STD_{Binary}=207 mJ$), taking into account the measurements errors and the OS activity.

\begin{figure}
    \center{\includegraphics[width=.9\linewidth]{imgs/docvsbin}}
    \caption{Comparing the variation of binary and Docker versions of aggregated \textsf{LU}, \textsf{CG} and \textsf{EP} benchmarks}\label{fig:docker}
\end{figure}
